Untitled

### 2023-10-12 code/analysis_Redo.Rmd
small changes
adding lots of new event study plots for Access analysis

```{r}
# dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
# uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")
# clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
#   #filter(Year >= included.years[1]) %>% 
#   group_by(Zip, Year) %>%
#   summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
#   arrange(desc(Clinics))
```

@@

df.temp

did2s(
      data = dfc.new %>% 
        inner_join(dfc %>% filter(Year == 2010 & Total < 14000 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Altman", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )

@@

set.seed(234)  #232
df.spill2 <- df.spill2 %>% 
  group_by(Zip) %>% 
  mutate(Dist = ifelse(is.na(Dist), sample(dist.vecs, 1, replace = T), Dist), 
                                  Att.viz = ifelse(Att == 0, rep(sample(c(2012:2021), 1, replace = T), each = 1), Att)) %>% 
  mutate(Dist.rounded = as.factor(ceiling(Dist / 10)))

@@

p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE))%>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid.control = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = NumberofPatients - NumberofPatients.control, 
         `Patients - Medicaid` = NumberofPatients_Medicaid - NumberofPatients_Medicaid.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Unadjusted DID Estimates by Distance to Competitive Zip")

@@

  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(Zip != '04401')
# ,
#          Unemployed = Unemployed / Unemp_denom,
#          Elderly = Age65andOver / TotalPop,
#          Black = Black / TotalPop,
#          Hispanic = Hispanic / TotalPop)

@@

event_study(data = df.spill3, 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) <= 7) %>% 
  #filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")
```

## Access by quantile
```{r}
qnats1 <- c(0, 0.2, 0.4, 0.6, 0.8)
qnats2 <- c(0.2, 0.4, 0.6, 0.8, 1)

qnats1 <- seq(0, 0.8, by = 0.2)
qnats2 <- seq(0.2, 1, by = 0.2)

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist > quantile(Dist, qnats1[1]) & Dist < quantile(Dist, qnats2[1])), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    TEs <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 2:5){
      model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist < quantile(Dist, qnats2[i])), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      TEs <- rbind(TEs, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

    df.spill3 %>% filter(Zip != '04401')
```

@@

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Rival") %>% 
  mutate(DistRivaltoCenter = sqrt((xcoor - popcenter.x)^2 + (ycoor - popcenter.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(Radius = mean.nas(Radius), DistRivaltoCenter = mean.nas(DistRivaltoCenter))

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Incumbent") %>% 
  mutate(DistIncumbtoCenter = sqrt((xcoor - popcenter.x)^2 + (ycoor - popcenter.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(Radius = mean.nas(Radius), DistIncumbtoCenter = mean.nas(DistIncumbtoCenter))

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Incumbent") %>%
  select(Zip, xcoor, ycoor) %>% 
  full_join(df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Rival") %>%
  select(Zip, xcoor, ycoor), by = c("Zip")) %>% 
  mutate(DistIncumbtoRival = sqrt((xcoor.x - xcoor.y)^2 + (ycoor.x - ycoor.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(DistIncumbtoRival = mean.nas(DistIncumbtoRival))

>>>>

```{r}
dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 40, Access))
clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

uds.sites.full %>%
  filter(is.na(Zip))
```

@@

did2s(
      data = dfc.new %>% 
        inner_join(dfc %>% filter(Year == 2010 & Total > 14000 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )

@@

set.seed(234)  #234
df.spill2 <- df.spill2 %>% 
  group_by(Zip) %>% 
  mutate(Dist = ifelse(is.na(Dist), sample(dist.vecs, 1, replace = T), Dist), 
                                  Att.viz = ifelse(Att == 0, rep(sample(c(2012:2021), 1, replace = T), each = 1), Att)) %>% 
  mutate(Dist.rounded = as.factor(ceiling(Dist / 10)))

@@

p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE))%>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid.control = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = NumberofPatients - NumberofPatients.control, 
         `Patients - Medicaid` = NumberofPatients_Medicaid - NumberofPatients_Medicaid.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  filter(Dist.rounded < 210) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + #xlim(0, 200) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Unadjusted DID Estimates by Distance to Competitive Zip")

@@

  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
  #mutate(Sites = log(Sites + 1)) %>% 
  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(Zip != '04401')
# ,
#          Unemployed = Unemployed / Unemp_denom,
#          Elderly = Age65andOver / TotalPop,
#          Black = Black / TotalPop,
#          Hispanic = Hispanic / TotalPop)

@@

## Event study plots
```{r}

ev.pop1 <- event_study(data = df.spill3, 
  yname = "Medicaid", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicaid")
ev.pop2 <- event_study(data = df.spill3, 
  yname = "Medicare", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicare")
ev.pop3 <- event_study(data = df.spill3, 
  yname = "Uninsured", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Uninsured")
ev.pop4 <- event_study(data = df.spill3, 
  yname = "Private", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Private")

ggarrange(ev.pop1, ev.pop2, ev.pop3, ev.pop4, common.legend = TRUE, ncol = 1)

## Access by quantile
```{r}
qnats1 <- seq(0, 0.75, by = 0.25)
qnats2 <- seq(0.25, 1, by = 0.25)

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    TEs <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:4){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "SL", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      TEs <- rbind(TEs, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Sites in Farthest 20% of Zips")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Sites in Competitive Zip")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Hours in Farthest 20% of Zips")

zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Hours in Competitive Zip")

zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
zp

did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% 
  group_by(Tx) %>% 
  summarise(mean(Sites))

@@

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Rival") %>% 
  mutate(DistRivaltoCenter = sqrt((xcoor - popcenter.x)^2 + (ycoor - popcenter.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(Radius = mean.nas(Radius), SD = sd(DistRivaltoCenter, na.rm = TRUE), DistRivaltoCenter = mean.nas(DistRivaltoCenter))

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Incumbent") %>% 
  mutate(DistIncumbtoCenter = sqrt((xcoor - popcenter.x)^2 + (ycoor - popcenter.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(Radius = mean.nas(Radius), SD = sd(DistIncumbtoCenter, na.rm = TRUE), DistIncumbtoCenter = mean.nas(DistIncumbtoCenter))

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Incumbent") %>%
  select(Zip, xcoor, ycoor) %>% 
  full_join(df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Rival") %>%
  select(Zip, xcoor, ycoor), by = c("Zip")) %>% 
  mutate(DistIncumbtoRival = sqrt((xcoor.x - xcoor.y)^2 + (ycoor.x - ycoor.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(SD = sd(DistIncumbtoRival, na.rm = TRUE), DistIncumbtoRival = mean.nas(DistIncumbtoRival))
